Visual proteomics using whole-lamella 2D template matching

### 2022-02-23 manuscript.tex
Mostly work on figure 1 [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/db1bd1a285c0519196fc92fb04c4ad271adf3006.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/db1bd1a285c0519196fc92fb04c4ad271adf3006/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1890188788

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/16c528a690632e78c5557a0164f560eef13aa854/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/16c528a690632e78c5557a0164f560eef13aa854}{jojoelfe/deco\_lace\_template\_matching\_manuscript@16c528a}
on February 23, 2022.

@@

Understanding of cellular processes requires knowledge of the amounts, location,
interactions, and conformations of biomolecules inside the cell. Techniques that
measure this can broadly be divided into label- and label-free techniques. In
label-techniques a probe is physically attached to a molecule is interest that
is able to produce a high signal-to-noise signal, such as a fluorescent molecule.
In label-free techniques the physical properties of molecules themselves are
used for detection. An example for this is proteomics using mass-spectrometry
{[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage of label-free techniques is that
they can provide information over thousands of molecules, while label-techniques
offer higher fidelity information for a few molecules. Especially spatial
information can most of the time only be achieved using label-techniques, such
as fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.

@@

\begin{figure}
\hypertarget{fig:initmatching}{%
\centering
\includegraphics{figures/figure1_draft.pdf}
\caption{Template matching of ribosomal large subunits in fib-milled neutrophil like cells}\label{fig:initmatching}
}
\end{figure}

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/db1bd1a285c0519196fc92fb04c4ad271adf3006/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/db1bd1a285c0519196fc92fb04c4ad271adf3006}{jojoelfe/deco\_lace\_template\_matching\_manuscript@db1bd1a}
on February 23, 2022.

@@

Understanding of cellular processes requires knowledge of the amounts, location,
interactions, and conformations of biomolecules inside the cell. Techniques that
measure this can broadly be divided into label- and label-free techniques. In
label-techniques a probe is physically attached to a molecule of interest that
is able to produce a high signal-to-noise signal, such as a fluorescent molecule.
In label-free techniques the physical properties of molecules themselves are
used for detection. An example for this is proteomics using mass-spectrometry
{[}\protect\hyperlink{ref-tSXIKPl7}{1}{]}. The advantage of label-free techniques is that
they can provide information over thousands of molecules, while label-techniques
offer higher fidelity information for a few molecules. Especially spatial
information can most of the time only be achieved using label-techniques, such
as fluorescence microscopy {[}\protect\hyperlink{ref-VBmW7Aot}{2}{]}.

@@

\begin{figure}
\hypertarget{fig:initmatching}{%
\centering
\includegraphics{figures/initmatching.pdf}
\caption{2D template matching of the large subunit of the ribosome in fib-milled neutrophil-like cells
(A) Overview image of the lamella. Major cellular regions are labeled, as Nucleus (Nuc), Mitochondria (M), and granular cytoplasm (GrCyt). FOVs where high-magnification images for template matching where acquired are indicated as boxes with the number of matches indicated on the bottom right. FOVs displayed in Panels B-E are color-coded.
(B-E) FOVs with projection of ribosome LSU matches shown in green. (B) Perinuclear region, the only matches are in the cytoplasmic half. (C) Cytoplasmic region with high density of ribosomes (D) Mitochondrium, as expected there are only matches in the cytoplasmic region (E) Cytoplasm, with low density of ribosomes.}\label{fig:initmatching}
}
\end{figure}
